Dual host-parasite transcriptomes of apicomplexan Eimeria falciformis and its natural mouse host

### 2016-07-29 figuresANDmanuscript/manuscriptBMCformat/manuscript_rnaseq.tex
+1 merge of chnges in MS, removed ugly table 1...

  \subsection*{Additional file 2 --- Results of statistical tests (edgeR) }
  Fold-changes, p-values and false discovery rates (adjusted p-values)
  are given for all tested contrasts (one compressed csv file).

>>>>

  \subsection*{Additional file 2 --- Results of statistical tests (edgeR) }
  Focal contrast, fold-changes, likelihood ratio in/excluding this
  difference in models, p-values , and false discovery rates (adjusted
  p-values) are given for all tested contrasts (one compressed csv
  file).
